Searching for flaring star-planet interactions in star-planet systems in Kepler and TESS

### 2023-01-31 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{figure*}[ht!]
    \script{paper_adtext_vs_value_scatterplots.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/PAPER_ADtest_vs_p_spi_erg_s_bp0.png}
        \caption{
            Expected power of SPI vs. AD test results, assuming an unmagnetized planet. These results are mainly dominated by the X-ray luminosity of the host star, see Fig.~\ref{fig:adtest_xray_flux_erg_s}. Assuming a magnetized planet with $B_p=1$ G has only minor influence on the results shown in this figure, see Appendix.
        }
        \label{fig:adtest_p_spi_erg_s_bp0}
    \end{centering}
\end{figure*}

\begin{figure*}[ht!]
    \script{paper_adtext_vs_value_scatterplots.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/PAPER_ADtest_vs_xray_flux_erg_s.png}
        \caption{X-ray luminosity of the host star~\cite{foster2022identifying} vs. AD test results.
        }
        \label{fig:adtest_xray_flux_erg_s}
    \end{centering}
\end{figure*}

@@

\begin{figure*}[ht!]
    \script{paper_adtext_vs_value_scatterplots.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/PAPER_ADtest_vs_p_spi_erg_s.png}
        \caption{
            Expected power of SPI vs. AD test results, same as Fig.~\ref{fig:adtest_p_spi_erg_s_bp0}, but assuming a magnetized planet with $B_p=1$ G. 
        }
        \label{appendix:fig:adtest_p_spi_erg_s}
    \end{centering}
\end{figure*}

>>>>

% \begin{figure*}[ht!]
%     \script{paper_adtext_vs_value_scatterplots.py}
%     \begin{centering}
%         \includegraphics[width=\linewidth]{figures/PAPER_ADtest_vs_p_spi_erg_s_bp0.png}
%         \caption{
%             Expected power of SPI vs. AD test results, assuming an unmagnetized planet. These results are mainly dominated by the X-ray luminosity of the host star, see Fig.~\ref{fig:adtest_xray_flux_erg_s}. Assuming a magnetized planet with $B_p=1$ G has only minor influence on the results shown in this figure, see Appendix.
%         }
%         \label{fig:adtest_p_spi_erg_s_bp0}
%     \end{centering}
% \end{figure*}

% \begin{figure*}[ht!]
%     \script{paper_adtext_vs_value_scatterplots.py}
%     \begin{centering}
%         \includegraphics[width=\linewidth]{figures/PAPER_ADtest_vs_xray_flux_erg_s.png}
%         \caption{X-ray luminosity of the host star~\cite{foster2022identifying} vs. AD test results.
%         }
%         \label{fig:adtest_xray_flux_erg_s}
%     \end{centering}
% \end{figure*}

@@

\begin{figure*}[ht!]
    \script{paper_adtext_vs_value_scatterplots.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/PAPER_ADtest_vs_p_spi_erg_s_sab_wBp_colorcode_dist.png}
        \caption{
            Expected power of SPI from stretch and break vs. AD test results, assuming a magnetized planet with $B_p=1$ G. 
        }
        \label{appendix:fig:adtest_p_spi_erg_s}
    \end{centering}
\end{figure*}
